Arrows for Parallel Computations

### 2017-07-09 paper/content/futures.tex
removed notion of the MVar future from the paper

For our |Par| Monad and Multicore Haskell backends, we can simply use |MVar|s \cite{jones1996concurrent} (Fig.~\ref{fig:MVarFuture}), as in a shared memory setting we do not require Eden's sophisticated communication channels. \fixme{explain MVars}
\begin{figure}[tb]
\begin{code}
{-# NOINLINE putUnsafe #-}

putUnsafe :: a -> MVar a
putUnsafe a = unsafePerformIO $ do
    mVar <- newEmptyMVar
    putMVar mVar a
    return mVar

instance (NFData a) => Future MVar a where
    put = arr putUnsafe
    get = arr takeMVar >>> arr unsafePerformIO
\end{code}
\caption{A |MVar| instance of the |Future| typeclass for the |Par| Monad and Multicore Haskell backends.}
\label{fig:MVarFuture}
\end{figure} % $

>>>>

For our |Par| Monad and Multicore Haskell backends, we can simply use |BasicFuture|s (Fig.~\ref{fig:BasicFuture}) which are just simple wrappers around the actual data, as in a shared memory setting we do not require Eden's sophisticated communication channels.
\begin{figure}[tb]
\begin{code}
data BasicFuture a = BF a

instance (NFData a) => NFData (BasicFuture a) where
    rnf (BF a) = rnf a

instance (NFData a) => Future BasicFuture a where
    put = arr BF
    get = arr (\(BF a) -> a)
\end{code}
\caption{The |BasicFuture| type and its |Future| instance for the |Par| Monad and Multicore Haskell backends.}
\label{fig:BasicFuture}
\end{figure} % $
